Wavelets

### 2019-04-08 Exploring/wavelets.Rmd
housekeeping

```{r}
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

@@

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
SACTN_fyears <- SACTN_fyears %>%
  dplyr::rename(temp = insitu_temp)

@@

temp.d <- temp.d(df = SACTN_fyears) 
# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
# temp.d <- temp.d(df = K10_fyears)

>>>>

```{r}
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2012, 2015)) %>% 
  drop_na()
}

@@

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
# SACTN_fyears <- SACTN_fyears %>%
#   dplyr::rename(temp = insitu_temp)

@@

# temp.d <- temp.d(df = SACTN_fyears) 
# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
temp.d <- temp.d(df = K10_fyears)
